---
title: "BBets"
output: html_document
autor: Andrew Arredondo
date: "2024-09-27"
---


This assignment has three questions:  

1. in a class of 35 students, Dr. J bets $1 against student's $1  that at least 2 students have the same birthday, month, day.
Find the probability thatat least two student have the same birthday.  If 26 students in the class take the bet how much is Dr. J expected to win/lose.   How much should Dr. J wager against the student's $1 to make this a fair bet?

2. Assume class size is 26 instead of 35.  With the same bet ($1 ot $1) what is the probability Dr. J wins the bet now.  If 20 of the 26 students make the bet, what is Dr. J's expected profit/loss?

3. What size class (how many students) makes the $1 againt $1 a fair bet?



```{r setup, include=FALSE}
set.seed(123)  # Set seed for reproducibility
library(ggplot2)
```

```{r}
# Function to simulate the birthday problem
birthday_simulation <- function(n_people = 35, n_simulations = 100) {
  count <- 0
  for (i in 1:n_simulations) {
    birthdays <- sample(1:365, n_people, replace = TRUE)  # Sample birthdays
    if (length(unique(birthdays)) < n_people) {
      count <- count + 1  # Count if there's a duplicate
    }
  }
  return(count / n_simulations)  # Return probability
}

# Run the simulation
n_simulations <- 100
probabilities <- replicate(n_simulations, birthday_simulation())

# Print the probabilities

```

```{r}
# Plot the histogram of the probabilities
ggplot(data.frame(probabilities), aes(x = probabilities)) +
  geom_histogram(binwidth = 0.05, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Birthday Problem Probabilities",
       x = "Probability",
       y = "Frequency") +
  theme_minimal()

```

```{r}
mean_prob <- mean(probabilities)
cat('mean = ', mean_prob, "\n")

```

```{r}
conf_interval <- quantile(probabilities, probs = c(0.025, 0.975))
cat('95% Confidence Interval = [', conf_interval[1], ', ', conf_interval[2], ']', "\n")

```

```{r}
EV= mean_prob*26-(1-mean_prob)*26
print(paste("ev-",EV))
```


```{r}
FAIR=(mean_prob)/(1-mean_prob)
print(paste("fairbet-",FAIR))
```

## question 2
```{r}
# Function to simulate the birthday problem
birthday_simulation <- function(n_people = 26, n_simulations = 100) {
  count <- 0
  for (i in 1:n_simulations) {
    birthdays <- sample(1:365, n_people, replace = TRUE)  # Sample birthdays
    if (length(unique(birthdays)) < n_people) {
      count <- count + 1  # Count if there's a duplicate
    }
  }
  return(count / n_simulations)  # Return probability
}

# Run the simulation
n_simulations <- 100
probabilities <- replicate(n_simulations, birthday_simulation())

# Print the probabilities

```
```{r}
mean_prob <- mean(probabilities)
cat('mean = ', mean_prob, "\n")

```
```{r}
EV= mean_prob*20-(1-mean_prob)*20
print(paste("ev-",EV))
```





## question 3
```{r}
class_size=22
```
```{r}
# Function to simulate the birthday problem
birthday_simulation <- function(n_people = class_size, n_simulations = 100) {
  count <- 0
  for (i in 1:n_simulations) {
    birthdays <- sample(1:365, n_people, replace = TRUE)  # Sample birthdays
    if (length(unique(birthdays)) < n_people) {
      count <- count + 1  # Count if there's a duplicate
    }
  }
  return(count / n_simulations)  # Return probability
}

# Run the simulation
n_simulations <- 100
probabilities <- replicate(n_simulations, birthday_simulation())
mean_prob=mean(probabilities)
# Print the probabilities
print(paste("prob=",mean_prob))
```
